\systemEnding: Bootstrapping Domain-Specific Languages for Neurally-Guided Bayesian Program Learning

### 2018-11-28 archive.tex
soundness completeness theorems

\newcommand{\Expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em E}}
\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
\newcommand{\shift}[1]{\uparrow^{#1}}
\newcommand{\substitute}[2]{[\$ #1 \mapsto #2]}
\newcommand{\reduce}{\longrightarrow}
\newcommand{\manyReduce}{\longrightarrow^*}

\newtheorem{definition}{Definition}

@@

Over the course of 5 wake/sleep iterations,
the system authors a DSL
containing parametric and, sometimes, higher-order drawing routines,
allowing it to write programs for objects like
polygons, circles, spirals, and snowflakes.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/logo90.png}
  \caption{LOGO graphics tasks. The agent must learn to write programs that draw these 90 pictures.}\label{everyLogo}
\end{figure}
\begin{figure}
\centering  \begin{tabular}{c|c}
      \includegraphics[width = 0.5\textwidth]{figures/initialDreams/montage.png}&
  \includegraphics[width = 0.5\textwidth]{figures/finalDreams/montage.png}
    \end{tabular}
  \caption{Dreams, or samples, from the DSL before (left) and after (right) training on tasks in Figure~\ref{everyLogo}. Blue: where the agent started drawing. Pink: where the agent ended drawing.}\label{logoDreams}
\end{figure}

@@

@@

We apply \system to learning generative models for images and text (Fig.~\ref{geomCompiled}-\ref{regularExpressions}).
For images, we learn programs controlling a simulated ``pen,''
and the task is to look at an image and explain it in terms of a graphics program.
For text, we learn probabilistic regular expressions -- a simple probabilistic program for which inference is always tractable -- and the task is to
infer a regex from a collection of strings.
\begin{figure}[t]
  \includegraphics[width=\columnwidth]{figures/geomCompiled.eps} 
  \caption{
  Top left: Example training tasks. Top right: samples from the learned DSL.
 Bottom: \% holdout testing tasks solved (middle); on the sides are averaged samples from the DSL
  before any training (left) and after last iteration (right).}\label{geomCompiled}

  \end{figure}

\begin{figure}
\centering
\tiny
\tabcolsep=2pt
\vspace{0pt}
\begin{tabular}{cc}
\begin{tabular}{ccc}
\multicolumn{3}{c}{Tasks:}\\
\hline
1.14531&F&110.9 \\ 
?&CL&163.2 \\
1.29857&F&207.3\\
?&PCFL&143.3 \\
\multicolumn{3}{c}{Learned generative models:}\\
\hline
 \scode{\textbackslash?\textbar(1\textbackslash .\textbackslash d+)}& \scode{((\textbackslash u\textbackslash u)*)\textbar F}& \scode{\textbackslash d\textbackslash d\textbackslash d\textbackslash.\textbackslash d} \\
 \multicolumn{3}{c}{Samples from synthesized generative models:}\\
\hline
1.61&DQDF& 343.8 \\ 
?&F&241.2\\
?&F&647.5\\
1.2&KI&246.8\\
1.5080987&F&728.6\\
?&GL&029.3\\
1.453&F&289.1\\
    \hline
        \\
\end{tabular} 
&
\begin{tabular}{c}
\begin{tabular}{l}
\multicolumn{1}{c}{Learned DSL:}\\
\hline
$f_1() = $ \scode{\textbackslash u\textbackslash w*}\\
$f_2(x) = $ \scode{($x$|$f_1$)*} $=$ \scode{($x$|\textbackslash u\textbackslash w*)*}\\
$f_3(x) =  f_2(\scode{space}) = $\scode{( \textbar\textbackslash u\textbackslash w*)*}\\
\hline
$f_4(x) = $ \scode{($x$*$x$)}\\
\emph{ (equivalent to regex `plus')}\\
$f_5() = f_4(\scode{\textbackslash l}) = \scode{\textbackslash l*\textbackslash l}$\\
    \hline
\end{tabular}
\\
\\
\includegraphics[width=.4\linewidth]{figures/nampiregexjoshcurve3.eps} 
\end{tabular}
\end{tabular}
\vspace{-.3cm}
\caption{regex stuff}
\end{figure}

@@

\subsection{Refactoring code with version spaces}\label{appendixVersion}
Recall that our goal is to define an operator over version spaces, $I\beta_n$,
which calculates the set of $n$-step refactorings.
We define this operator recursively as follows:
\begin{align*}
  I\beta_n(v)& = \uplus \left\{ \underbrace{I\beta'(I\beta'(I\beta'(\cdots}_{i \text{ times}} v))) \;:\; 0\leq i \leq n \right\}\\
  I\beta'(v)& = \uplus \left\{(\lambda b)v\;:\;v\mapsto b\in S_0(v)\text{, when }v\not=\Lambda \right\}\cup
  \begin{cases}
    \text{if $v$ is a primitive or index:}&\varnothing\\
    \text{if $v = \lambda b$:}&\lambda I\beta'(b)\\
    \text{if $v = (f\;x)$:}&(I\beta'(f)\;I\beta'(x))\\
  \end{cases}
  \\
  S_k(v)& = \left\{\shift{k}v\mapsto \$k \right\}\cup
  \begin{cases}
    \text{if $v$ is primitive:}&\left\{\Lambda\mapsto v \right\}\\    
    \text{if $v = \$i$ and $i < k$:}&\left\{\Lambda\mapsto \$i \right\}\\
    \text{if $v = \$i$ and $i\geq k$:}&\left\{\Lambda\mapsto \$(i + 1) \right\}\\
    \text{if $v = \lambda b$:}&\left\{v'\mapsto \lambda b' \;:\; v'\mapsto b'\in S_{k + 1}(b)  \right\}\\
    \text{if $v = (f\;x)$:}&\left\{v_1\cap v_2\mapsto (f'\;x') \;:\; v_1\mapsto f'\in S_k(f),\; v_2\mapsto x'\in S_k(x) \right\}\\
    \text{if $v = \uplus V$:}&\bigcup_{v'\in V}S_n(v')\\
    \text{if $v$ is $\varnothing$:}&\varnothing\\
    \text{if $v$ is $\Lambda$:}&\left\{\Lambda\mapsto\Lambda \right\}
  \end{cases}
\end{align*}
where $\shift{k}$ is the shifting operator~\cite{pierce},
which adds $k$ to all of the free variables in a $\lambda$-expression or version space.
We have written the definition of $I\beta_n$ recursively,
but implement it using a dynamic program:
we hash cons each version space,
and only calculate the operators $I\beta_n$,
$I\beta'$, and $S_k$ once per each version space.
Refactoring is similarly done more quickly with dynamic programming (see Equation~\ref{FACTORING} for the recursive definition of \textsc{refactor}).

@@

\begin{figure}[h]
\centering
%  \includegraphics{figures/iterations.eps}
\begin{tikzpicture}
  \begin{scope}[shift={(2.5,0)}]
    \node[obs] at (3,3) (dx){$\mathcal{D}$};
    \node[latent] at (3.5,1.75) (zp){$p$};
%    \node[obs] at (4,3) (tx){$\theta^{(x)}$};
    \node[obs] at (3.5,0.7) (xp) {$x$};
    \node[align = center] at ([yshift = -0.6cm,xshift = 0.5cm]xp.south) {Wake: Infer $p$};
    \draw [->,red] (xp.east) to[out = 0,in = 90] node(nn){} (zp.north);
%    \draw [->,red] (tx) -- (zp);
    \draw [->] (dx) -- (zp);
    \node at (nn) {
      \begin{tikzpicture}[x=2.5cm,y=1.25cm,transform canvas={scale=0.2,shift={+(-1,2.5)}}]
        \tikzstyle{neuron}=[circle,fill=blue!50,minimum size=20pt]
        \fill[fill=white] (-0.25,-0.5) rectangle (2.25,-4.5);
        \node[rectangle] at (1,1) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (I-\name) at (0,-\y) {};
        \foreach \name / \y in {1,...,3}
            \node[neuron] (H-\name) at (1,-\y-0.5) {};
        \foreach \name / \y in {1,...,4}
            \node[neuron] (O-\name) at (2,-\y) {};
        \foreach \source in {1,...,4}
            \foreach \dest in {1,...,3}
                \draw [-latex] (I-\source) -- (H-\dest);
        \foreach \source in {1,...,3}
            \foreach \dest in {1,...,4}
                \draw [-latex] (H-\source) -- (O-\dest);
      \end{tikzpicture}
    };
    \node[shift={+(0,-0.65)}] at (nn) [fill=white]{ $q(x)$ };
  \end{scope}

  \begin{scope}[shift={(0.7,-4.2)}]
    \node[obs] at (3,3) (dt){$\mathcal{D},\theta$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]dt.south) (p2){$p_2$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]p2.south) (x2){$x_2$};
    \draw [->] (p2.south) -- (x2.north);
    \draw [->] (dt.south) -- (p2.north);

    \node[obs] at ([yshift = 0cm,xshift = -0.5cm]p2.west) (p1){$p_1$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]p1.south) (x1){$x_1$};
    \draw [->] (p1.south) -- (x1.north);
    \draw [->] (dt.south) -- (p1.north);

    \node[obs] at ([yshift = 0cm,xshift = 0.5cm]p2.east) (p3){$p_3$};
    \node[obs] at ([yshift = -0.7cm,xshift = 0.0cm]p3.south) (x3){$x_3$};
    \draw [->] (p3.south) -- (x3.north);
    \draw [->] (dt.south) -- (p3.north);

    \node at ([yshift = 0cm,xshift = 0.3cm]p3.east) {$\cdots $};
    \node at ([yshift = 0cm,xshift = 0.3cm]x3.east) {$\cdots $};

    \node[obs] at ([yshift = 0cm,xshift = 1.3cm]p3.east) (zp){$p$};
    \node[obs] at ([yshift = 0cm,xshift = 1.3cm]x3.east) (xp) {$x$};
    \draw [->] (zp.south) -- (xp.north);
    \plate {}{(zp)(xp)}{$x\in X$};

    \draw[dashed,cyan,very thick] ([yshift = 0.5cm,xshift = -2]p1.west)
    rectangle  ([yshift = -0.45cm,xshift = +2]xp.east);
    \node[align = center] at ([yshift = -1cm,xshift = 0.6cm]x2.south) {Sleep-R: Train $q$\\training data: cyan $(x,p)$};
  \end{scope}

  \begin{scope}[shift={(7.7,-4)}]
    \node[latent] at (0.5,3) (d){$\mathcal{D}$};
    \node[latent] at (1.5,3) (t){$\theta$};
    \node[obs] at (1,1.75) (z){$p$};
%     \node[latent] at (3.5,1.5) (tx){$\theta^{(x)}$};
    \node[obs] at (1,0.5) (x) {$x$};
    \edge {z}{x};
    \edge {d,t}{z};
    \plate {}{(z)(x)}{$x\in X$};
    \node[align = center] at ([yshift = -1cm]x.south) {Sleep-G: Induce $(\mathcal{D},\theta)$};
  \end{scope}

\end{tikzpicture}
\end{figure}
\end{document}

>>>>

\newcommand{\Expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\indicator}{\mathds{1}} %{{\rm I\kern-.3em E}}
\newcommand{\expect}{\mathds{E}} %{{\rm I\kern-.3em E}}
\newcommand{\probability}{\mathds{P}} %{{\rm I\kern-.3em P}}
\newcommand{\shift}[1]{\uparrow^{#1}}
\newcommand{\downshift}[1]{\downarrow^{#1}}
\newcommand{\substitute}[2]{[\$ #1 \mapsto #2]}
\newcommand{\reduce}{\longrightarrow}
\newcommand{\manyReduce}{\longrightarrow^*}

\newtheorem{definition}{Definition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

@@

Over the course of 5 wake/sleep iterations,
the system authors a DSL
containing parametric and, sometimes, higher-order drawing routines,
allowing it to write programs for objects like
polygons, circles, spirals, and snowflakes.
Figure~\ref{logoPrimitives}
illustrates several learned DSL subroutines.
Once it has synthesized these new subroutines,
the agent generates a rich and highly varied
data set of dreams on which to train the recognition model.
Figure~\ref{logoDreams}
illustrates  dreams before and after learning ---
one sees that
the system has learned to recombine
the building blocks and motifs in the training data.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/logo90.png}
  \caption{LOGO graphics tasks. The agent must learn to write programs that draw these 90 pictures.}\label{everyLogo}
\end{figure}
\begin{figure}
\centering  \begin{tabular}{cc}
    \toprule
    Parametric drawing routines&Higher-order drawing routine\\\midrule
    \begin{tabular}{rl}
      Semicircle:& \raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_24.png}}\\
      Spiral:&\raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_25.png}}\\
      Greek Spiral:&\raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_10.png}}\\
      S-Curves:&\raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_11.png}}        \\
        Polygons \& Stars:
&\raisebox{-.5\height}{\includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_12.png}}
    \end{tabular}
    &
    \begin{tabular}{c}
      Repeat and rotate subprogram:\\
          \includegraphics[width = 0.3\textwidth]{figures/logo_primitives/logo_primitive_18.png}
      \end{tabular}

    \\\bottomrule 
  \end{tabular}
  \caption{Example primitives learned by \system when trained on tasks in Figure~\ref{everyLogo}. Agent learns parametric routines for drawing families of curves (left) as well as subroutines that take entire programs as input (right). Each row of images on the left is the same code executed with different parameters. Each image on the right is the same code executed with different parameters and with a different subprogram provided as input.}\label{logoPrimitives}
  \end{figure}
\begin{figure}
\centering  \begin{tabular}{c|c}
      \includegraphics[width = 0.5\textwidth]{figures/initialDreams/montage.png}&
  \includegraphics[width = 0.5\textwidth]{figures/finalDreams/montage.png}
    \end{tabular}
  \caption{Dreams, or samples, from the DSL before (left) and after (right) training on tasks in Figure~\ref{everyLogo}. Blue: where the agent started drawing. Pink: where the agent ended drawing.}\label{logoDreams}
\end{figure}

@@

Inspired by the classic AI `copy task' --- where an agent must look at
an image of a tower made of toy blocks and re-create the
tower~\cite{towerCopy} --- we give \system 112 tower `copy tasks'
(Figure~\ref{towerTasks}).  Here the agent observes both an image of a
tower and the locations of each of its blocks, and must write a
program that plans how a simulated hand would build the tower.
These towers are built from Lego-style blocks
that snap together on a discrete grid (e.g., we do not model gravity
and discretize the coordinates of the blocks).

The system starts out with four domain-specific primitives:
\code{left} and \code{right}, which take an integer $n$ as input and
move the hand left/right $n$ Lego grid spaces; along with
\code{horizontal} and \code{vertical}, which put down
horizontal/vertical Lego blocks.  As with LOGO graphics we also
include our two standard planning primitives (\code{for} and
\code{get/set}).
Starting with this basis
the system can only solve
12.5\% of the copy tasks.
With successive wake/sleep cycles
we assemble a DSL containing
parametric option-like subroutines (Figure~\ref{towerPrimitives}),
allowing the agent to solve 90\% of the tasks.
\begin{figure}
  \includegraphics[width = \textwidth]{figures/every_tower.png}
  \caption{}\label{towerTasks}
\end{figure}
\begin{figure}
  \caption{Learned subroutines for building towers out of Lego-style blocks when trained on tasks in Figure~\ref{towerTasks}. These subroutines act like parametric options~\cite{options},
  giving higher-level building blocks that the agent can use to plan.}
  \end{figure}

@@

We apply \system to learning generative models for images and text (Fig.~\ref{geomCompiled}-\ref{regularExpressions}).
For images, we learn programs controlling a simulated ``pen,''
and the task is to look at an image and explain it in terms of a graphics program.
For text, we learn probabilistic regular expressions -- a simple probabilistic program for which inference is always tractable -- and the task is to
infer a regex from a collection of strings.

@@

\subsection{Refactoring code with version spaces}\label{appendixVersion}
Recall that our goal is to define an operator over version spaces, $I\beta_n$,
which calculates the set of $n$-step refactorings.
We define this operator recursively as follows:
\begin{align*}
  I\beta_n(v)& = \uplus \left\{ \underbrace{I\beta'(I\beta'(I\beta'(\cdots}_{i \text{ times}} v))) \;:\; 0\leq i \leq n \right\}\\
  I\beta'(v)& = \uplus \left\{(\lambda b)v\;:\;v\mapsto b\in S_0(v)\text{, when }v\not=\Lambda \right\}\cup
  \begin{cases}
    \text{if $v$ is a primitive or index:}&\varnothing\\
    \text{if $v = \lambda b$:}&\lambda I\beta'(b)\\
    \text{if $v = (f\;x)$:}&(I\beta'(f)\;I\beta'(x))\\
  \end{cases}
  \\
  S_k(v)& = \left\{\downshift{k}_0v\mapsto \$k \right\}\cup
  \begin{cases}
    \text{if $v$ is primitive:}&\left\{\Lambda\mapsto v \right\}\\    
    \text{if $v = \$i$ and $i < k$:}&\left\{\Lambda\mapsto \$i \right\}\\
    \text{if $v = \$i$ and $i\geq k$:}&\left\{\Lambda\mapsto \$(i + 1) \right\}\\
    \text{if $v = \lambda b$:}&\left\{v'\mapsto \lambda b' \;:\; v'\mapsto b'\in S_{k + 1}(b)  \right\}\\
    \text{if $v = (f\;x)$:}&\left\{v_1\cap v_2\mapsto (f'\;x') \;:\; v_1\mapsto f'\in S_k(f),\; v_2\mapsto x'\in S_k(x) \right\}\\
    \text{if $v = \uplus V$:}&\bigcup_{v'\in V}S_n(v')\\
    \text{if $v$ is $\varnothing$:}&\varnothing\\
    \text{if $v$ is $\Lambda$:}&\left\{\Lambda\mapsto\Lambda \right\}
  \end{cases}\\
  \downshift{k}_c \$i& = \$i\text{, when $i < c$}\\
  \downshift{k}_c \$i& = \$(i - k)\text{, when $i\geq c + k$}\\
  \downshift{k}_c \$i& = \varnothing \text{, when $c\leq i <  c + k$}\\
  \downshift{k}_c \lambda b &= \lambda\downshift{k}_{c + 1}b\\
  \downshift{k}_c (f\;x)& = (\downshift{k}_cf\;\downshift{k}_cx)\\
  \downshift{k}_c \uplus V& = \uplus \left\{\downshift{k}_c v \;|\;v\in V \right\}\\
  \downshift{k}_c v& = v\text{, when }v\text{ is a primitive or }\varnothing \text{ or }\Lambda
\end{align*}
where $\shift{k}$ is the shifting operator~\cite{pierce},
which adds $k$ to all of the free variables in a $\lambda$-expression or version space.
We have written the definition of $I\beta_n$ recursively,
but implement it using a dynamic program:
we hash cons each version space,
and only calculate the operators $I\beta_n$,
$I\beta'$, and $S_k$ once per each version space.
Refactoring is similarly done more quickly with dynamic programming (see Equation~\ref{FACTORING} for the recursive definition of \textsc{refactor}).

We now formally proved that $I\beta$ exhaustively enumerates the space of possible refactorings.
Our approach is to first prove that $S_k$ exhaustively enumerates
the space of possible substitutions that
could give rise to a program.
The following pair of technical lemmas are useful; both are easily proven by structural induction.
\begin{lemma}
  Let $e$ be a program or version space and $n$, $c$ be natural numbers. \\Then $\shift{-1}_{n + c}\shift{n + 1}_ce = \shift{n}_c e$,
  and in particular $\shift{-1}_{n}\shift{n + 1}e = \shift{n} e$.
\label{neutralizeShift}\end{lemma}
\begin{lemma}
  Let $e$ be a program or version space and $n$, $c$ be natural numbers. \\Then $\downshift{n}_{c}\shift{n}_ce =  e$,
  and in particular $\downshift{n}\shift{n}e =  e$.
  \label{neutralizeDown}
\end{lemma}

\begin{theorem}
  \textbf{Consistency of $S_n$}. \\If $(v\mapsto b)\in S_n(u)$ then
  for every $v'\in v$ and $b'\in b$ we have $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b'\in u$.
\end{theorem}
\begin{proof}
  Suppose $b = \$n$ and therefore, by the definition of $S_n$, also $v = \downshift{n}_0 u$.
  Invoking Lemmas~\ref{neutralizeShift} and~\ref{neutralizeDown}
  we know that $u = \shift{-1}_n\shift{n + 1}v$
  and so for every $v'\in v$ we have $\shift{-1}_n\shift{n + 1}v'\in u$.
  Because $b = \$n = b'$ we can rewrite this to $\shift{-1}_n[\$n\mapsto \shift{n + 1}v']b'\in u$.

  Otherwise assume $b\not= \$n$ and proceed by structural induction on $u$:

  \begin{itemize}
  \item If $u = \$i < n$ then we have to consider the case that $v = \Lambda$ and $b = u = \$i = b'$.
    Pick $v'\in \Lambda$ arbitrarily. Then $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b' = \shift{-1}_n\$i = \$i\in u$.
  \item If $u = \$i\geq n$ then we have consider the case that $v = \Lambda$ and $b = \$(i + 1) = b'$.
    Pick $v'\in \Lambda$ arbitrarily. Then $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b' = \shift{-1}_n\$(i + 1) = \$i\in u$.
  \item If $u$ is primitive then we have to consider the case that $v = \Lambda$ and $b = u = b'$.
    Pick $v'\in \Lambda$ arbitrarily. Then $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b' = \shift{-1}_nu = u\in u$.
  \item If $u$ is of the form $\lambda a$,
    then $S_n(u)\subset\left\{v\mapsto \lambda b\;|\; (v\mapsto b)\in S_{n + 1}(a) \right\}$.
    Let $v\mapsto \lambda b\in S_n(u)$.
    By induction for every $v'\in v$ and $b'\in b$ we have $\shift{-1}_{n + 1}[\$n\mapsto \shift{2 + n}v']b'\in a$,
    which we can rewrite to $\shift{-1}_{n}[\$n\mapsto \shift{1 + n}v']\lambda b'\in \lambda a = u$.
  \item If $u$ is of the form $(f\;x)$ then
    then $S_n(u)\subset\left\{v_f\cap v_x\mapsto (b_f\;b_x)\;|\; (v_f\mapsto b_f)\in S_{n}(f),\;(v_x\mapsto b_x)\in S_{n}(x) \right\}$.
    Pick $v'\in v_f\cap v_x$ arbitrarily.
    By induction for every $v_f'\in v_f$, $v_x'\in v_x$, $b_f'\in b_f$, $b_x'\in b_x$
    we have $\shift{-1}_{n}[\$n\mapsto \shift{1 + n}v_f'] b_f' \in f$ and $\shift{-1}_{n}[\$n\mapsto \shift{1 + n}v_x'] b_x' \in x$.
    Combining these facts gives
    $\shift{-1}_{n}[\$n\mapsto \shift{1 + n}v'] (b_f'\;b_x') \in (f\;x) = u$.
  \item If $u$ is of the form $\uplus U$ then
    pick $(v\mapsto b)\in S_n(u)$ arbitrarily.
    By the definition of $S_n$ there is a $z$ such that $(v\mapsto b)\in S_n(z)$,
    and the theorem holds immediately by induction.
  \item If $u$  is $\varnothing $ or $\Lambda$ then the theorem holds vacuously.
    \end{itemize}
\end{proof}
\begin{theorem}
  \textbf{Completeness of $S_n$}.\\
  If there exists programs $v'$  and $b'$, and a version space $u$, such that $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b'\in u$,
  then there also exists $(v\mapsto b)\in S_n(u)$ such that $v'\in v$ and $b'\in b$.
\end{theorem}
\begin{proof}
  As before we first consider the case that $b' = \$n$.
  If so then
  $\shift{-1}_n\shift{1 + n}v'\in u$ or (invoking Lemma~\ref{neutralizeShift}) that $\shift{n}v'\in u$
  and (invoking Lemma~\ref{neutralizeDown}) that $v'\in \downshift{n}u$.
  From the definition of $S_n$ we know that $(\downshift{n}u\mapsto \$n)\in S_n(u)$ which is what was to be shown.

  Otherwise assume that $b'\not=\$n$. Proceeding by structural induction on $u$:
  \begin{itemize}
  \item If $u = \$i$ then,
    because $b'$ is not $\$n$,
    we have $\shift{-1}_nb' = \$i$.
    Let $b' = \$j$,
    and so
    $$
    i =
    \begin{cases}
      j&\text{ if }j < n\\
      j - 1&\text{ if }j > n
    \end{cases}
    $$
    where $j = n$ is impossible because by assumption $b'\not=\$n$.

    If $j < n$ then
    $i = j$ and so $u = b'$.
    By the definition of $S_n$ we have
    $(\Lambda\mapsto \$i)\in S_n(u)$,
    completing this inductive step because $v'\in \Lambda$ and $b'\in \$i$.
    Otherwise assume $j > n$
    and so $\$i = \$(j - 1) = u$.
    By the definition of $S_n$ we have
    $(\Lambda\mapsto \$(i + 1))\in S_n(u)$,
    completing this inductive step because $v'\in \Lambda$
    and $b' = \$j = \$(i + 1)$.
  \item If $u$ is a primitive then,
    because $b'$ is not $\$n$,
    we have $\shift{-1}_nb' = u$,
    and so $b' = u$.
    By the definition of $S_n$ we have $(\Lambda\mapsto u)\in S_n(u)$
    completing this inductive step because $v'\in \Lambda$ and $b' = u$.
  \item If $u$ is of the form $\lambda a$ then,
    because of the assumption that $b'\not=\$n$,
    we know that $b'$ is of the form $\lambda c'$ 
    and that $\lambda \shift{-1}_{n + 1}[\$(n + 1)\mapsto \shift{2 + n}v']c'\in \lambda a$.
    By induction this means that there is a $(v\mapsto c)\in S_{n + 1}(a)$
    satisfying $v'\in v$ and $c'\in c$.
    By the definition of $S_n$ we also know that
    $(v\mapsto  \lambda c)\in S_n(u)$,
    completing this inductive step because $b' = \lambda c'\in \lambda c$.
  \item If $u$ is of the form $(f\;x)$
    then,
    because of the assumption that $b'\not=\$n$,
    we know that $b'$ is of the form $(b_f'\;b_x')$
    and that both
    $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b_f'\in f$ and $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b_x'\in x$.
    Invoking the inductive hypothesis twice
    gives a
    $(v_f\mapsto b_f)\in S_n(f)$ satisfying $v'\in v_f$, $b_f'\in b_f$
    and a
    $(v_x\mapsto b_x)\in S_n(x)$ satisfying $v'\in v_x$, $b_x'\in b_x$.
    By the definition of $S_n$
    we know that $(v_f\cap v_x\mapsto b_f\;b_x)\in S_n(u)$
    completing the inductive step because $v'$ is guaranteed to be
    in both $v_f$ and $v_x$ and we know that
    $b' = (b_f'\;b_x')\in (b_f\;b_x)$.

  \item If $u$ is of the form $\uplus U$
    then there must be a $z\in U$ such that $\shift{-1}_n[\$n\mapsto \shift{1 + n}v']b'\in z$.
    By induction there is a $(v\mapsto b)\in S_n(z)$ such that $v'\in v$ and $b'\in v$.
    By the definition of $S_n$ we know that $(v\mapsto b)$ is also in $S_n(u)$ completing the inductive step.
  \item If $u$  is $\varnothing $ or $\Lambda$ then the theorem holds vacuously.    
    \end{itemize}
\end{proof}

@@

\begin{table*}%[t!]
  \makebox[\textwidth][c]{
    \scriptsize
  \tabcolsep=4pt
  \renewcommand\code\texttt
  \renewcommand\codechar[1]{\texttt{"#1"}}
  \newcommand{\helpSize}{0.25cm}
  \begin{tabular}{cccc}
    \toprule
    &{\normalsize Symbolic regression}&{\normalsize Laws of motion}&\\\midrule
    \rotatebox[origin=c]{90}{\normalsize \pop{Programs} \& Tasks}&{\tabcolsep=7pt
    \begin{tabular}{cc}
      \includegraphics[width = 3em]{figures/functions/4.png}&
      \includegraphics[width = 3em]{figures/functions/146}\\
      \pop{\code{$f($x$) = $($f_1$ x)}}&    \pop{\code{$f($x$) = $($f_6$ x)}}\\
      ~\\
      \includegraphics[width = 3em]{figures/functions/112.png}&
        \includegraphics[width = 3em]{figures/functions/92.png}
      \\
      \pop{\code{$f($x$) = $($f_4$ x)}}&    \pop{\code{$f($x$) = $($f_3$ x)}}\\

    \end{tabular}
    }
    &
    \begin{tabular}{cc}
      \includegraphics[width = 15em]{figures/massOnSpring.png} &
            \includegraphics[width = 15em]{figures/planets.png}
      \\
      \begin{tabular}{l}
              \blueCode{$f($o,$\Delta) = $($f_3$ o $\Delta$}\\
      \hspace{1cm}\blueCode{(- (* $k$ (pos o))}\\
      \hspace{1cm}\phantom{\code{(- }}\blueCode{(* $-9.8$ $\hat{x}$)))}\\
      \end{tabular}&
      \begin{tabular}{l}
              \blueCode{$f($a,b,$\Delta) = $($f_3$ a $\Delta$}\\
      \hspace{1cm}\blueCode{(/ (* $G$ (mass a) (mass b))}\\
      \hspace{1cm}\phantom{\code{(- }}\blueCode{(square (- (pos a) (pos b)))))}\\
        \end{tabular}
      \end{tabular}
    &

    ~\\
    \midrule
    \rotatebox[origin=c]{90}{\normalsize \popp{DSL}}&
      \begin{tabular}{l}
    \popp{$f_0($\code{x}$)\,=\,$\code{(+ x real)}}\\
    \popp{$f_1($\code{x}$)\,=\,$\code{($f_0$ (* real x))} }\\
    \popp{$f_2($\code{x}$)\,=\,$\code{($f_1$ (* x (}$f_0$\code{ x)))}}\\
    \popp{$f_3($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_2$\code{ x)))}}\\
    \popp{$f_4($\code{x}$)\,=\,$\code{($f_0$ (* x (}$f_3$\code{ x)))}}\\
    \hspace{\helpSize}\emph{($f_4$: 4th order polynomial)}\\
    \popp{$f_5($\code{x}$)\,=\,$\code{(/ real x)}}\\
    \popp{$f_6($\code{x}$)\,=\,$\code{($f_5$ ($f_0$ x))}}\\
    \hspace{\helpSize}\emph{($f_6$: rational function)}\\

  \end{tabular}
      &
      \begin{tabular}{l}
        \greenCode{$f_0($\code{o},$\Delta)\, = \,$(set-pos o (+ (pos o) (* $\Delta$ (vel o))))}\\
        \hspace{\helpSize}\emph{($f_0$: integrates position)}\\
        \greenCode{$f_1($\code{o},\code{a},$\Delta)\, = \,$(set-vel o (+ (vel o) (* $\Delta$ a)))}\\
        \hspace{\helpSize}\emph{($f_1$: integrates velocity)}\\
        \greenCode{$f_2($\code{o},\code{F}$)\, = \,$(/ F (mass o))}\\
        \hspace{\helpSize}\emph{($f_2$: Newton's second law)}\\
        \greenCode{$f_3($\code{o},$\Delta$,\code{F}$)\, = \,$($f_0$ o $\Delta$ ($f_1$ o ($f_2$ o F) $\Delta$))}\\
        \hspace{\helpSize}\emph{($f_3$: applies Newton's second law and integrates)}

        \end{tabular}

&

  \\\bottomrule\\
\end{tabular}}\vspace{-0.5cm} 
\caption{Top: Tasks from three domains we apply our algorithm to, each followed by the programs \system discovers for them. Bottom: Several examples from learned DSL. Notice that learned DSL primitives can call each other, and that \system rediscovers higher-order functions like \code{filter} ($f_1$ under List Functions)}\label{initialExampleDSL}%\vspace{-0.5cm}
\end{table*}
\end{document}
